\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-04-14 forwards-and-backwards.tex
Update on Overleaf.

In Equation \eqref{eq: gamma-r convolution comparison}, we have established that 
$\rho_r(x-w) / \rho_\gamma(x-w) = C' \exp(-K (x-w)^2 / 2)$
with $K = \frac{1}{\epsilon_r^2} - \frac{1}{\epsilon_\gamma^2}$.
Therefore it suffices to show that for all $x,w \in \mathbb{R}^d$ and $s \in [0, 1/\theta]$, 
\begin{align} \label{eqn:goal3}
    F'(s) \exp\left(-A (x-w)^2 \right) \le C .
\end{align}

@@

\begin{definition}
    \label{def: MP definition of limit}
Let $F \in \mathcal{C}^{2}(\mathbb{R})$ and $f \in \mathcal{C}_{0}(\mathbb{R}^d)$.
We define $\Pgen$ to be a generator
acting on test functions of the form
$F_f(\eta):=F (\langle f, \eta \rangle)$
such that 
\begin{equation}
\begin{aligned}
\Pgen^{\infty} F_f(\eta):=& F'(\langle f, \eta \rangle)
                   \times \left\{
                   \big\langle
                        \gamma(x, \smooth{\gamma} \eta(x))
                            \mathcal{B}\left(
                            f(\cdot) r(\cdot, \smooth{r} \eta(\cdot))
                            \right)(x)
                    +
                    f(x)
                        F(x, \smooth{F} \eta(x)),
                        \eta(dx)
                    \big\rangle
                   \right\}\\
                &+ \frac{1}{2}F''(\langle f, \eta \rangle)
                  \times \left\{
                  \alpha \big\langle
                    \gamma\left( x, \smooth{\gamma} \eta(x) \right)
                    r\left(x, \smooth{r} \eta(x) \right)
                    f^2(x),
                    \eta (dx)
                    \big\rangle 
                  \right\}.
\end{aligned}    
\end{equation}
We define $(\eta^{\infty}(t))_{t \geq 0}$ to be the solution to the Martingale Problem $(\Pgen^{\infty}, \eta_0)$, i.e. 
for all $F \in \mathcal{C}^{2}(\mathbb{R})$
and $f \in \mathcal{C}_{0}(\mathbb{R}^d)$,
$$M_t:=F_f(\eta^{\infty}_t)-F_f(\eta_0)#
-\int_{0}^{t}\Pgen^{\infty}F_f(\eta^{\infty}_s)ds$$
is a martingale.
\end{definition}
\begin{remark}
Taking $F(x)=x$ and $F(x)=x^2$, we can recover Equation \eqref{eqn:mgale_problem} and \eqref{eqn:mgale_variation}.
\end{remark}
\begin{lemma}[Convergence of generators for the population process]
As $\theta \to \infty$,
$(\eta^{\theta}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_f(\mathbb{R}^d))$
to $(\eta^{\infty}(t))_{t \geq 0}$.
\end{lemma}
\begin{proof}
We use Theorem 4.8.10 in \cite{EK}.
First of all, the set of functions
$\{F_f(\eta):= F(\langle f, \eta \rangle ),~
F \in \mathcal{C}^{2}(\mathbb{R}), ~
f \in \mathcal{C}_{0}(\mathbb{R}^d)\}$
is a dense and convergence-determining 
subset of functions in $\mathcal{M}_f(\mathbb{R}^d)$.
Therefore, it suffices to show that for any $t>0$,
\begin{equation}
    \label{eq: Convergence Condition}
\lim_{\theta \to \infty}
\mathbb{E}\left[
\left(
F_f(\eta^{\theta}_{t+s})-F_f(\eta^{\theta}_t)
-\int_{t}^{t+s}\Pgen^{\infty}F_f(\eta^{\theta}_s)ds
\right)
\prod_{i=1}^{k}\langle h_i,\eta^{\theta}_{t_i} \rangle
\right]=0
\end{equation}
for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+s$,
and $h_1,...,h_k \in \mathcal{C}_{0}(\mathbb{R}^d)$.

To prove this,
we apply Taylor's series expansion
and make use of the Martingale Problem characterisation
of $\eta^{\theta}_T$.
We have
\begin{equation}
\begin{aligned}
&\mathbb{E}\left[F_f(\eta^{\theta}_{t+s})-F_f(\eta^{\theta}_t)\bigg| \mathcal{F}_t \right]\\
=& F'(\langle f, \eta^{\theta}_t \rangle )
\mathbb{E}\left[
                \langle f, \eta^{\theta}_{t+s}\rangle
                    -\langle f, \eta^{\theta}_t\rangle 
                    \bigg| \mathcal{F}_t
         \right]
+\frac{1}{2}F''(\langle f, \eta^{\theta}_t \rangle )
\mathbb{E}\left[
                \left(
                    \langle f, \eta^{\theta}_{t+s}\rangle -\langle f, \eta^{\theta}_t\rangle
                \right)^2
                \bigg| \mathcal{F}_t
        \right]\\
&+\frac{1}{6}F'''(\langle f, \eta^{\theta}_{t+s'}\rangle)\mathbb{E}\left[
                \left(
                    \langle f, \eta^{\theta}_{t+s}\rangle -\langle f, \eta^{\theta}_t\rangle
                \right)^3
                \bigg| \mathcal{F}_t
        \right]\\
=& F'(\langle f, \eta^{\theta}_t \rangle )\\
& \times  \int_{0}^{t}\bigg\{
        \int\left(   \int \theta
     \left(
        f(z)r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
            -f(x)r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
            \right)
                    q_\theta(x,dz)\right)
        \\ & \qquad \qquad \qquad \qquad {} \times
                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                            \eta^{\theta}_{s}(dx)
     \\ & \qquad \qquad {} +\int 
     f(x)F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
     \eta^{\theta}_{s}(dx)
    \bigg\} ds\\
=+\frac{1}{2}F''(\langle f, \eta^{\theta}_t \rangle )\\
&\times 
\end{aligned}
\end{equation}
\end{proof}

>>>>

In Equation \eqref{eq: gamma-r convolution comparison}, we have established that 
$\rho_r(x-w) / \rho_\gamma(x-w) = C' \exp(-K (x-w)^2 / 2)$
with $K = \frac{1}{\epsilon_r^2} - \frac{1}{\epsilon_\gamma^2}$.
Therefore it suffices to show that for all $x,w \in \mathbb{R}^d$ and $s \in [0, 1/\theta]$, 
\begin{align} 
    F'(s) \exp\left(-A (x-w)^2 \right) \le C .
\end{align}

@@

\begin{definition}
    \label{def: MP definition of limit}
Let $F \in \mathcal{C}^{2}(\mathbb{R})$ and $f \in \mathcal{C}_{0}(\mathbb{R}^d)$.
We define $\Pgen$ to be a generator
acting on test functions of the form
$F_f(\eta):=F (\langle f, \eta \rangle)$
such that 
\begin{equation}
\begin{aligned}
\Pgen^{\infty} F_f(\eta):=& F'(\langle f, \eta \rangle)
                   \times \left\{
                   \big\langle
                        \gamma(x, \smooth{\gamma} \eta(x))
                            \mathcal{B}\left(
                            f(\cdot) r(\cdot, \smooth{r} \eta(\cdot))
                            \right)(x)
                    +
                    f(x)
                        F(x, \smooth{F} \eta(x)),
                        \eta(dx)
                    \big\rangle
                   \right\}\\
                &+ \frac{1}{2}F''(\langle f, \eta \rangle)
                  \times \left\{
                  \alpha \big\langle
                    \gamma\left( x, \smooth{\gamma} \eta(x) \right)
                    r\left(x, \smooth{r} \eta(x) \right)
                    f^2(x),
                    \eta (dx)
                    \big\rangle 
                  \right\}.
\end{aligned}    
\end{equation}
We define $(\eta^{\infty}(t))_{t \geq 0}$ to be the solution to the Martingale Problem $(\Pgen^{\infty}, \eta_0)$, i.e. 
for all $F \in \mathcal{C}^{2}(\mathbb{R})$
and $f \in \mathcal{C}_{0}(\mathbb{R}^d)$,
$$M_t:=F_f(\eta^{\infty}_t)-F_f(\eta_0)
-\int_{0}^{t}\Pgen^{\infty}F_f(\eta^{\infty}_s)ds$$
is a martingale.
\end{definition}
\begin{remark}
Taking $F(x)=x$ and $F(x)=x^2$, we can recover Equation \eqref{eqn:mgale_problem} and \eqref{eqn:mgale_variation}.
\end{remark}
\begin{lemma}[Convergence of generators for the population process]
As $\theta \to \infty$,
$(\eta^{\theta}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}(\mathcal{M}_f(\mathbb{R}^d))$
to $(\eta^{\infty}(t))_{t \geq 0}$.
\end{lemma}
\begin{proof}
We use Theorem 4.8.10 in \cite{EK}.
First of all, the set of functions
$\{F_f(\eta):= F(\langle f, \eta \rangle ),~
F \in \mathcal{C}^{2}(\mathbb{R}), ~
f \in \mathcal{C}_{0}(\mathbb{R}^d)\}$
is a dense and convergence-determining 
subset of functions in $\mathcal{M}_f(\mathbb{R}^d)$.
Therefore, it suffices to show that for any $t>0$,
\begin{equation}
    \label{eq: Convergence Condition}
\lim_{\theta \to \infty}
\mathbb{E}\left[
\left(
F_f(\eta^{\theta}_{t+s})-F_f(\eta^{\theta}_t)
-\int_{t}^{t+s}\Pgen^{\infty}F_f(\eta^{\theta}_s)ds
\right)
\prod_{i=1}^{k}\langle h_i,\eta^{\theta}_{t_i} \rangle
\right]=0
\end{equation}
for all $k\geq 0$, $0\leq t_1<t_2<...,t_k \leq t < t+s$,
and $h_1,...,h_k \in \mathcal{C}_{0}(\mathbb{R}^d)$.

To prove this,
we apply Taylor's series expansion
and make use of the Martingale Problem characterisation
of $\eta^{\theta}_T$.
We have
\begin{equation}
\begin{aligned}
&\mathbb{E}\left[F_f(\eta^{\theta}_{t+s})-F_f(\eta^{\theta}_t)\bigg| \mathcal{F}_t \right]\\
=& F'(\langle f, \eta^{\theta}_t \rangle )
\mathbb{E}\left[
                \langle f, \eta^{\theta}_{t+s}\rangle
                    -\langle f, \eta^{\theta}_t\rangle 
                    \bigg| \mathcal{F}_t
         \right]
+\frac{1}{2}F''(\langle f, \eta^{\theta}_t \rangle )
\mathbb{E}\left[
                \left(
                    \langle f, \eta^{\theta}_{t+s}\rangle -\langle f, \eta^{\theta}_t\rangle
                \right)^2
                \bigg| \mathcal{F}_t
        \right]\\
&+\frac{1}{6}F'''(\langle f, \eta^{\theta}_{t+s'}\rangle)\mathbb{E}\left[
                \left(
                    \langle f, \eta^{\theta}_{t+s}\rangle -\langle f, \eta^{\theta}_t\rangle
                \right)^3
                \bigg| \mathcal{F}_t
        \right]\\
=& F'(\langle f, \eta^{\theta}_t \rangle )\\
& \times  \int_{0}^{t}\bigg\{
        \int\left(   \int \theta
     \left(
        f(z)r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
            -f(x)r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
            \right)
                    q_\theta(x,dz)\right)
        \\ & \qquad \qquad \qquad \qquad {} \times
                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                            \eta^{\theta}_{s}(dx)
     \\ & \qquad \qquad {} +\int 
     f(x)F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
     \eta^{\theta}_{s}(dx)
    \bigg\} ds\\
=+\frac{1}{2}F''(\langle f, \eta^{\theta}_t \rangle )\\
&\times \frac{\theta}{N} \int_{0}^{t}\bigg\{
\langle \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
\int f^2(y)r\big(y,\rho_{r}*\eta^{\theta}_{s}(y)\big)q_\theta(x,dy) 
,\eta^{\theta}_{s}(dx)\rangle\\
& \qquad \qquad +\langle \mu\big(x,\eta^{\theta}_{s}\big)f^2(x) 
,\eta^{\theta}_{s}(dx)\rangle \bigg\}ds.
\end{aligned}
\end{equation}
\end{proof}
